The relativistic capture of compact objects by intermediate-mass black holes

### 2019-06-03 mn.tex
work on 1st section

Due to the fact that the IMBH is lighter than a supermassive black hole in a
galactic nucleus, we cannot assume anymore that it is fixed at the centre of
the system. This makes an analytical study of the problem arduous and
challenging.  In this article we model the potential formation of an IMRI in a
dense stellar system, a cluster, via the interactions between an IMBH and
stellar-mass black holes. The outcome of such process is varied and could lead
to different end states, including the formation of an IMRI, a stellar-mass
black hole binary, the ejection of one or both stellar-mass black holes, or
even a head-on collision between the compact objects.  To this end, we use a
direct-summation $N-$body code that includes post-Newtonian to account for the
periapsis shift and the loss of energy via gravitational radiation \citep[as
presented for the first time in][]{KupiEtAl06}, as well as the cluster
gravitational potential \textbf{(REF: Manuel, your first fork of ARCHAIN cited
here)}. We scan the parameter space, in particular the IMBH and stellar-mass
black hole masses, their orbital configuration, and the host cluster structural
properties with a set of 2,000 models.

@@

In this work, we study IMRIs formation via triple interactions involving an
IMBH and two stellar mass BHs that inhabit in the centre of a massive star
cluster.  One of the two BHs is bound to the IMBH, while the second BH orbits
around the IMBH-BH binary centre of mass. The triple orbital configuration can
be dissected into an inner and an outer binary, as sketched in Figure
\ref{fig:f1}. This simple picture is complicated by the fact that the triple
cannot be considered as an isolated system, as other cluster members can affect
its evolution.

\begin{figure}
    \centering
    \includegraphics[width=7cm]{triple}
    \caption{Sketch of the IMBH-BH-BH triple configuration.}
    \label{fig:f1}
\end{figure}

Therefore, the phase space that characterises the triple's main properties can be dissected into three groups:
\begin{itemize}
    \item {\bf Inner binary (IMBH+BH)}: depends on the IMBH and BH masses, $M_\ibh$ and $M_\bhu$, the binary semi-major axis $a_\inn$ and its eccentricity $e_\inn$.
    \item {\bf Outer binary (IMBH+BH+BH)}: depends on the third BH mass, $M_\bhd$, semi-major axis $a_\out$, eccentricity $e_\out$.
    \item {\bf Host cluster}: we model the host cluster as a \cite{Deh93} sphere, characterized by total mass, $M_c$, scale radius, $r_c$, and the inner slope of the density profile $\gamma$.
\end{itemize}

In order to unveil the link between IMRIs formation and IMBH properties, we select the IMBH mass among eight different values ${\rm Log}(M_\ibh/\Ms) = 2-2.5-3-3.5-4-4.5-5-5.5$. This range covers typical values of putative IMBH masses forming in stellar systems of various sizes, from young and open clusters, to globular clusters, and up to low-mass nuclear clusters and dwarf galaxies.

Stellar BH masses are selected between $M_{\rm min} = 10\Ms$ and $M_{\rm max} = 30\Ms$, a mass range typical of stellar environments with a metallicity $Z<0.25\Zs$ \citep{belczynski16,spera16}. 
From Figure 5 of \cite{belczynski16}, we find that the BH mass can be connected to the initial star mass via a simple power-law 
\begin{equation}
\left(\frac{m_\bh}{\Ms}\right) = A(Z) \left(\frac{m_*}{\Ms}\right)^{C(Z)} + B(Z),
\end{equation}
with the coefficient depending on the metallicity as summarized in Table \ref{tab:t1}.

>>>>

Due to the fact that the IMBH is lighter than a supermassive black hole in a
galactic nucleus, we cannot assume anymore that it is fixed at the centre of
the system. This makes an analytical study of the problem arduous and
challenging.  In this article we model the potential formation of an IMRI in a
dense stellar system, a cluster, via the interactions between an IMBH and
stellar-mass black holes. The outcome of such process is varied and could lead
to different end states, including the formation of an IMRI, a stellar-mass
black hole binary, the ejection of one or both stellar-mass black holes, or
even a head-on collision between the compact objects.  To this end, we use a
direct-summation $N-$body code that includes post-Newtonian to account for the
periapsis shift and the loss of energy via gravitational radiation \citep[as
presented for the first time in][]{KupiEtAl06}, as well as the cluster
gravitational potential \textbf{(REF: Manuel, your first fork of ARCHAIN cited
here)}. We scan the parameter space, in particular the IMBH and stellar-mass
black hole masses, their orbital configuration, and the host cluster structural
properties with a set of 2,000 models. \textbf{(Manuel, is the number right or did
you run more?)}

@@

Based on the numerical studies of
\cite{konstantinidis13,leigh14,MacLeodEtAl2016,haster16}, we consider a
stellar-mass black hole which has formed a binary with the IMBH and a second
stellar-mass black hole, orbiting around the binary centre-of-mass. We depict
this configuration in Figure~(\ref{fig:f1}) as an inner and outer binary, and
note that this triple configuration is not isolated, but embedded in a cluster.

\begin{figure}
    \centering
    \includegraphics[width=7cm]{triple}
    \caption{The inner binary is formed by the stellar-mass black hole of mass  $M_\ibh$ and $M_\bhu$, 
the binary semi-major axis $a_\inn$ and its eccentricity $e_\inn$. The outer binary depends on the mass of the
second stellar-mass black hole, $M_\bhd$, it has a semi-major axis  $a_\out$ and an eccentricity $e_\out$.
These three compact objects are embedded in a host cluster which is modelled following a Dehnen profile \citep{Deh93},
characterised by a total mass $M_c$, a scale radius, $r_c$, and the inner slope of the density profile $\gamma$. The angular
momentum of the inner binary $L_{\rm in}$ and the outer one $L_{\rm out}$ subtend and angle $i$.}
    \label{fig:f1}
\end{figure}

We choose the IMBH mass to range among eight different values ${\rm
Log}(M_\ibh/\Ms) = 2-2.5,\,3-3.5,\,4-4.5,\,5-5.5$, so as to cover typical values of
IMBH forming in stellar systems of various sizes, from young and open clusters,
to globular clusters, and up to low-mass nuclear clusters and dwarf galaxies.
Stellar-mass black hole (BH) masses are selected between $M_{\rm min} = 10\,\Ms$ and
$M_{\rm max} = 30\,\Ms$, a mass range typical of stellar environments with a
metallicity $Z<0.25\,\Zs$ \citep{belczynski16,spera16}.

From Figure 5 of \cite{belczynski16}, the BH mass can be connected to the
initial stellar mass via a simple power-law \textbf{(Manuel, didn't you derive
a similar result? why not credit yourself?)}

\begin{equation}
\left(\frac{m_\bh}{\Ms}\right) = A(Z) \left(\frac{m_*}{\Ms}\right)^{C(Z)} + B(Z),
\end{equation}

\noindent
with the coefficient depending on the metallicity as summarized in Table \ref{tab:t1}.
